---
title: "Legen-wait-for-it-dary!"
output: html_notebook
---

# Load Mons

Start by loading the CSV and doing some basic testing of the data.

## Data load
```{r}
library(tidyverse)
mons <- readr::read_csv('../data/orig/pokemon.csv')
mons %>% tally()
```

```{r}
mons <- mons %>%
  mutate(legendary = ifelse(is_legendary == 1, "legendary", "not legendary"))
```

Test for duplicate pokemons by looking for the same English name appearing more than once
```{r}
mons %>%
  select(name) %>%
  group_by(name) %>%
  tally() %>%
  filter(n > 1)
```
Okay, there are no duplicate entries in the data set.  I was worried there would be if types changed between generations for the same mon.

# Legendary EDA

## How many Pokemon are Legendary

```{r}
mons %>%
  group_by(legendary) %>%
  tally()
```

## Pokemon by height and weight

```{r}

mons %>%
  filter(!is.na(height_m) & !is.na(weight_kg)) %>%
  group_by(legendary) %>%
  summarise(mean_height = mean(height_m), mean_weight = mean(weight_kg))

mons %>%
  ggplot(aes(height_m, weight_kg)) +
  geom_point(aes(color = legendary))
```

## Pokemon by type
```{r}
mons %>%
  mutate(type1 = ifelse(is.na(type1), "none", type1),
         type2 = ifelse(is.na(type2), "none", type2)) %>%
  filter(type2 != "none") %>%
  group_by(type1, type2) %>%
  tally() %>%
  ggplot(aes(type1, type2)) +
  geom_tile(aes(fill = n))
```


# Classification Tree
## Split data
```{r}
library(caret)
set.seed(1501)
inTrain <- createDataPartition(y = mons$legendary,
                               p = 0.6,
                               list = FALSE)
training <- mons[inTrain,]
testing <- mons[-inTrain,]

training %>% 
  group_by(legendary) %>%
  tally()

testing %>% 
  group_by(legendary) %>%
  tally()
```


## Build tree
```{r}
library(rpart)
fit <- training %>%
  rpart(legendary ~ is_legendary,
        method = "class",
        data = .)
```

```{r}
predict(fit, testing)
```

